The Distributed Nature of Copycat..? (WIP)

### 2017-11-15 papers/paper.tex
Adds adjustment formulas and embeds them in paper
Adds initial writeup for adjustment formulas

The original formulas being used to do this were overly complicated.
In summary, many formulas were tested in a spreadsheet, and an optimal one was chosen that replicated the desired behavior.
[]

\lstinputlisting[language=Python]{test.py}

>>>>

The original formulas being used to do this were overly complicated.
In summary, many formulas were tested in a spreadsheet, and an optimal one was chosen that replicated the desired behavior.

The original formula for curving probabilties in copycat:
\lstinputlisting[language=Python]{formulas/original.py}

An alternative that seems to improve performance on the abd->abd xyz->? problem:
This formula produces probabilities that are not bounded between 0 and 1. These are generally truncated.
\lstinputlisting[language=Python]{formulas/entropy.py}

Ultimately, it wasn't clear to me that the so-called "xyz" problem should even be considered.
As discussed in [the literature], the "xyz" problem is a novel example of a cognitive obstacle. 
Generally, the best techniques for solving the "xyz" problem are discussed in the the publications around the "Metacat" project, which gives copycat a temporary memory and levels of reflection upon its actions.
However, it is possible that the formula changes that target improvement in other problems may produce better results for the "xyz" problem.
Focusing on the "xyz" problem, however, will likely be harmful to the improvement of performanace on other problems.

So, the original copycat formula is overly complicated, and doesn't perform optimally on several problems.
The entropy formula is an improvement, but other formulas are possible too.

Below are variations on a "weighted" formula.
The general structure is:

\[\emph{p'} = \frac{T}{100} * S + \frac{100-T}{100} * U\]

Where: $S$ is the convergence value for when $T = 0$ and
       $U$ is the convergence value for when $T = 100$.
The below formulas simply experiment with different values for $S$ and $U$
The values of $\alpha$ and $\beta$ can be used to provide additional weighting for the formula, but are not used in this section.

\lstinputlisting[language=Python]{formulas/weighted.py}

[Discuss inverse formula and why $S$ was chosen to be constant]

After some experimentation and reading the original copycat documentation, it was clear that $S$ should be chosen to be $0.5$ and that $U$ should implement the probability curving desired at high temperatures. 
The following formulas let $U = p^r$ if $p < 0.5$ and let $U = p^\frac{1}{r}$ if $p >= 0.5$.
This controls whether/when curving happens.
Now, the parameter $r$ simply controls the degree to which curving happens.
Different values of $r$ were experimented with (values between $10$ and $1$ were experimented with at increasingly smaller step sizes. 
$2$ and $1.05$ are both good choices at  opposite "extremes".
$2$ works because it is large enough to produce novel changes in behavior at extreme temperatures without totally disregarding the original probabilities.
Values above $2$ do not work because they make probabilities too uniform.
Values below $2$ (and above $1.05$) are feasible, but produce less curving and therefore less unique behavior.
$1.05$ works because it very closely replicates the original copycat formulas, providing a very smooth curving.
Values beneath $1.05$ essentially leave probabilities unaffected, producing no significant unique behavior dependent on temperature.

\lstinputlisting[language=Python]{formulas/best.py}

\newline

Random thought:
It would be interesting to not hardcode the value of $r$, but to instead leave it as a variable between $0$ and $2$ that changes depending on frustration.
However, this would be much like temperature in the first place....?
$r$ could itself be a function of temperature. That would be.... meta.... lol.
